\documentclass[a4paper,romanian,english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{color}
\usepackage{amssymb}
\usepackage{multirow} 
\usepackage[margin=1.5cm, top=-0.2cm]{geometry}% Makes margins narrower.
\definecolor{lg}{gray}{0.50}

\begin{document}
\title{Model Release Form}
\renewcommand{\today}{}
\maketitle{}
\pagenumbering{gobble} % Remove page numbers (and reset to 1)
\vspace{-0.8cm}

This agreement is between (please print):

\textcolor{lg}{(“Photographer”)}\\

and the following persons (please print):

\textcolor{lg}{(“Models”)}

\vspace{0.3cm}
I hereby grant to Photographer, his legal representatives, heirs and/or assigns, those for whom Photographer is acting, and those acting with his authority and permission (collectively “Photographer”),
the absolute right and permission to copyright and use, reuse, and publish:
\begin{itemize}
\renewcommand{\labelitemi}{$\Box$}
	\item All photographic portraits or pictures of me,
\end{itemize}
OR
\begin{itemize}
\renewcommand{\labelitemi}{$\Box$}
	\item Those photographic portraits or pictures of me identified by MD5 checksums below,
\end{itemize}
\noindent and all images resulting from these - in which I may or may not be included, in whole or in part, or composite or distorted in character or form, without restriction as to changes or alterations, 
in conjunction with my own or a fictitious name, or reproductions thereof in color or otherwise, made through any medium at his studios or elsewhere, and in any and all media now or hereafter known,
for art, advertising, trade, research, or any other legal purpose. 
I also consent to the use of any printed matter in conjunction therewith.
I hereby waive any right that I may have to inspect or approve the finished product or products or the advertising copy or printed matter that may be used in connection therewith or the use to which it may be applied.
I hereby release, discharge and agree to hold harmless Photographer from any and all liability that has or may occur or be produced in the taking of said pictures or any subsequent processing thereof, as well as any publication thereof.
I acknowledge that I am at least 18 years old, and have the right and ability to consent to the terms herein, and further, that I am authorized and able to sign on behalf of all persons listed above as
Model(s).
I understand that I am or may be giving up certain legal rights by signing this release.\\
\begin{center}
    MD5 checksums (if applicable):\vspace{0.1cm}
    \begin{tabular}{| c | c | c | c | c || c | c | c | c || c | c | c | c || c | c | c | c || c | c | c | c || c | c | c | c || c | c | c | c || c | c | c | c |}
	\hline
	\multirow{2}{*}{1}& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\cline{2-33}
	& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\hline \hline
	\multirow{2}{*}{2}& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\cline{2-33}
	& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\hline \hline
	\multirow{2}{*}{3}& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\cline{2-33}
	& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\hline \hline
	\multirow{2}{*}{4}& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\cline{2-33}
	& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\hline \hline
	\multirow{2}{*}{5}& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\cline{2-33}
	& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\hline \hline
	\multirow{2}{*}{6}& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\cline{2-33}
	& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\hline \hline
	\multirow{2}{*}{7}& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\cline{2-33}
	& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\hline \hline
	\multirow{2}{*}{8}& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\cline{2-33}
	& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\hline \hline
	\multirow{2}{*}{9}& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\cline{2-33}
	& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\hline \hline
	\multirow{2}{*}{10}& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\cline{2-33}
	& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
	\hline
    \end{tabular}
\end{center}
\begin{itemize}
\renewcommand{\labelitemi}{$\Box$}
	\item I have been duly informed on the nature of MD5 checksums, and understand that these accurately identify files.
	\item I have verified the correspondence of each checksum to the respective raw picture file.
	\centering \item I have read, understood, and agree to the terms of this release.
\end{itemize}\vspace{0.15cm}

Name (please print): \hfill Date: \hspace{4cm}

\vspace{0.4cm}
Signature:
\vfill
\end{document}
